---
title: "Graphs of ROI data"
output: html_notebook
---

This is the code to load in and graph the ROI data of the 24 subjects. 


```{r}
ROIdata <- fread("C:/Users/kgeier/Desktop/mayo/ROI data/AllContrasts_ROIs.csv")

```

Changing names of columns to be easier to read on graph
```{r}
colnames(ROIdata) <- c("SID", "Contrast", "R_MD", "L_MD", "R_Ant","L_Ant", "R_hipp", "L_hipp", "R_Fusi", "L_Fusi")
```



Finding average between left and right sides to make it less busy
```{r}
ROIdata$MD <-(ROIdata$L_MD + ROIdata$R_MD)/2 
ROIdata$Ant <-(ROIdata$L_Ant + ROIdata$R_Ant)/2 
ROIdata$Hipp <-(ROIdata$L_hipp + ROIdata$R_hipp)/2 
ROIdata$Fusi <-(ROIdata$L_Fusi + ROIdata$R_Fusi)/2 
```





Version with Left and Right averaged. 
```{r}
ROIdata %>%
  gather(c(`MD`:`Fusi`), key = "Name_of_ROI", value = "Tvalue") %>%
  group_by(Contrast) %>%
  #filter(!is.na(risk_carrier)) %>%
  ggplot(aes(y = Tvalue, x = Name_of_ROI, color = SID)) + 
  geom_boxplot() +
  #geom_point() +
  #geom_smooth(method = 'lm')+ 
  scale_x_discrete(limits=c("Ant","MD", "Hipp", "Fusi")) +
  facet_wrap(~Contrast, scales = 'free')+
    xlab("Name of ROI") +
    ylab("T Statistic")
```

Version with Left and Right split
```{r}
ROIdata %>%
  gather(c(`R_MD`:`L_hipp`), key = "Name_of_ROI", value = "Tvalue") %>%
  group_by(Contrast) %>%
  #filter(!is.na(risk_carrier)) %>%
  ggplot(aes(y = Tvalue, x = Name_of_ROI, color = SID)) + 
  geom_boxplot() +
  #geom_point() +
  #geom_smooth(method = 'lm')+ 
  scale_x_discrete(limits=c("R_Ant","L_Ant", "R_MD", "L_MD", "R_hipp", "L_hipp")) +
  facet_wrap(~Contrast, scales = 'free')
```

```{r}
ROI.s <- ROIdata[ROIdata$Contrast == 'Study_correct_vs_incorrect',]
ROI.tc <- ROIdata[ROIdata$Contrast == 'TestCue_Correct_vs_Incorrect',]
ROI.td <- ROIdata[ROIdata$Contrast == 'TestDelay_Correct_vs_Incorrect',]
ROI.tp <- ROIdata[ROIdata$Contrast == 'TestProbe_Correct_vs_Incorrect',]
```


Just study CorInc - Version with Left and Right averaged. 
```{r}
ROI.s %>%
  gather(c(`MD`:`Fusi`), key = "Name_of_ROI", value = "Tvalue") %>%
  #group_by(Contrast) %>%
  #filter(!is.na(risk_carrier)) %>%
  ggplot(aes(y = Tvalue, x = Name_of_ROI, color = SID)) + 
  geom_boxplot() +
  #geom_point() +
  #geom_smooth(method = 'lm')+ 
  scale_x_discrete(limits=c("Ant","MD", "Hipp", "Fusi")) +
  #facet_wrap(~Contrast, scales = 'free')+
    xlab("Name of ROI") +
    ylab("T Statistic") +
  ggtitle("Study Correct > Incorrect") +
  theme(plot.title = element_text(hjust = 0.5)) +
theme(text = element_text(size=44))
```

Just study CorInc - Version with Left and Right averaged. 
```{r}
ROI.tc %>%
  gather(c(`MD`:`Fusi`), key = "Name_of_ROI", value = "Tvalue") %>%
  #group_by(Contrast) %>%
  #filter(!is.na(risk_carrier)) %>%
  ggplot(aes(y = Tvalue, x = Name_of_ROI, color = SID)) + 
  geom_boxplot() +
  #geom_point() +
  #geom_smooth(method = 'lm')+ 
  scale_x_discrete(limits=c("Ant","MD", "Hipp", "Fusi")) +
  #facet_wrap(~Contrast, scales = 'free')+
    xlab("Name of ROI") +
    ylab("T Statistic") +
  ggtitle("Test Cue Correct > Incorrect") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size=44))
```

Just study CorInc - Version with Left and Right averaged. 
```{r}
ROI.td %>%
  gather(c(`MD`:`Fusi`), key = "Name_of_ROI", value = "Tvalue") %>%
  #group_by(Contrast) %>%
  #filter(!is.na(risk_carrier)) %>%
  ggplot(aes(y = Tvalue, x = Name_of_ROI, color = SID)) + 
  geom_boxplot() +
  #geom_point() +
  #geom_smooth(method = 'lm')+ 
  scale_x_discrete(limits=c("Ant","MD", "Hipp", "Fusi")) +
  #facet_wrap(~Contrast, scales = 'free')+
    xlab("Name of ROI") +
    ylab("T Statistic") +
  ggtitle("Test Delay Correct > Incorrect") +
  theme(plot.title = element_text(hjust = 0.5)) +
theme(text = element_text(size=44))
```

Just study CorInc - Version with Left and Right averaged. 
```{r}
ROI.tp %>%
  gather(c(`MD`:`Fusi`), key = "Name_of_ROI", value = "Tvalue") %>%
  #group_by(Contrast) %>%
  #filter(!is.na(risk_carrier)) %>%
  ggplot(aes(y = Tvalue, x = Name_of_ROI, color = SID)) + 
  geom_boxplot() +
  #geom_point() +
  #geom_smooth(method = 'lm')+ 
  scale_x_discrete(limits=c("Ant","MD", "Hipp", "Fusi")) +
  #facet_wrap(~Contrast, scales = 'free')+
    xlab("Name of ROI") +
    ylab("T Statistic") +
  ggtitle("Test Probe Correct > Incorrect") +
  theme(plot.title = element_text(hjust = 0.5)) +
theme(text = element_text(size=44))
```